Risk factors for severe COVID-19: a case-control study based on the Scottish population

### 2020-05-07 casecontrol.Rmd
Fixed to read ICD subchapters and BNF section codes

---
title: 'Risk factors for severe COVID-19 in Scotland: a population-based case-control study'
author: 
  - name: Paul M McKeigue
    email: paul.mckeigue@ed.ac.uk
    affiliation: Usher
  - name: Amanda Weir 
    affiliation: HPS
  - name: Jen Bishop
    affiliation: HPS
  - name: Stuart McGurnaghan
    affiliation: IGMM
  - name: Sharon Kennedy
    affiliation: HPS
  - name: Sharon Hutchinson 
    affiliation: GCU
  - name: David McAllister 
    affiliation: Glasgow
  - name: Chris Robertson 
    affiliation: Strathclyde
  - name: Rachael Wood
    affiliation: ISD
  - name: Nazir Lone
    affiliation: Usher
  - name: Tom Caparrotta 
    affiliation: IGMM
  - name: Helen M Colhoun
    affiliation: IGMM
address: 
   - code: Usher
     address: Usher Institute, College of Medicine and Veterinary Medicine, University of Edinburgh, Teviot Place, Edinburgh EH8 9AG, Scotland. PM - Professor of Genetic Epidemiology and Statistical Genetics. NL - Clinical Senior Lecturer in Critical Care
   - code: IGMM
     address: Institute of Genetics and Molecular Medicine, College of Medicine and Veterinary Medicine, University of Edinburgh, Western General Hospital Campus, Crewe Road, Edinburgh EH4 2XUC, Scotland. HC - Axa Chair in Medical Informatics and Epidemiology. TC - Sir George Alberti Doctoral Fellow in Pharmacoepidemiology. 
   - code: Glasgow
     address: Institute of Health and Wellbeing, University of Glasgow, 1 Lilybank Gardens, Glasgow G12 8RZ. DM - Senior Clinical Lecturer in Public Health 
   - code: HPS
     address: Health Protection Scotland (Public Health Scotland), Meridian Court, 5 Cadogan Street, Glasgow G2 6QE
   - code: Strathclyde
     address: Department of Mathematics and Statistics, University of Strathclyde, 16 Richmond Street, Glasgow G1 1XQ. CR - Professor of Public Health Epidemiology
   - code: GCU
     address: School of Health and Life Sciences, Glasgow Caledonian University. SH - Professor of Epidemiology and Population Health 
   - code: ISD
     address: NHS Information Services Division (Public Health Scotland), Gyle Square, 1 South Gyle Crescent, Edinburgh, EH12 9EB.  RW - Consultant in Maternal and Child Health.

@@

header-includes: |
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \usepackage{array}
output: 
#  pdf_document:
  rticles::plos_article:
    latex_engine: lualatex
    fig_caption: true
    keep_tex: true
#    toc: true
#    toc_depth: 2
csl: ../plos.csl
urlcolor: red

@@

@@

@@

### Comorbidities of initial interest

​
### Other recent health care exposure variables of interest are

Note that at this point we are not including high risk of exposure as covariates ie HCW, residential care home, prisoner etc this will form part of future work.

@@

@@

```{r demog, echo=FALSE, warning=FALSE, message=FALSE}
pvalue <- pvalue.latex(univariate.demog[, 5])
ci <- or.ci(univariate.demog[, 1], univariate.demog[, 3]) 
table.demog.aug <- data.frame(table.demog,
                                   ci, 
                                   pvalue)
colnames(table.demog.aug) <- c("Controls", "Cases", "Rate ratio (95% CI)", "p-value")
rownames(table.demog.aug) <- replace.names(rownames(table.demog.aug))

pander(table.demog.aug, 
       digits=c(0, 0, 3, 3, 3, 1),
       round=c(0, 0, 3, 3, 3, 10),
	   split.tables="Inf",
       align=rep("centre", 4), 
       split.cells=c(16, 16, 25, 8),
       caption="\\label{tab:demog}Univariate associations of severe disease with demographic factors")

@@

pvalue <- pvalue.latex(univariate.conditions[, 5])
ci <- or.ci(univariate.conditions[, 1], univariate.conditions[, 3]) 
table.conditions.aug <- data.frame(table.conditions,
                                   ci, 
                                   pvalue)
colnames(table.conditions.aug) <- c("Controls", "Cases", "Rate ratio (95% CI)", "p-value")
rownames(table.conditions.aug) <- replace.names(rownames(table.conditions.aug))

pander(table.conditions.aug, 
       digits=c(0, 0, 3, 3, 3, 1),
       round=c(0, 0, 3, 3, 3, 10),
	   split.tables="Inf",
       split.cells=c(20, 20, 20, 7),
       caption="\\label{tab:conditions}Univariate association of severe disease with comorbid conditions")

@@

pvalue <- pvalue.latex(univariate.drugs[, 5])
ci <- or.ci(univariate.drugs[, 1], univariate.drugs[, 3]) 
table.drugs.aug <- data.frame(table.drugs,
                                   ci, 
                                   pvalue)
colnames(table.drugs.aug) <- c("Controls", "Cases", "Rate ratio (95% CI)", "p-value")
rownames(table.drugs.aug) <- replace.names(rownames(table.drugs.aug))

pander(table.drugs.aug, 
       digits=c(0, 0, 3, 3, 3, 1),
       round=c(0, 0, 3, 3, 3, 10),
	   split.tables="Inf",
       split.cells=c(20, 20, 20, 7), 
       caption="\\label{tab:drugs}Univariate association of severe disease with drugs prescribed in last year")

@@

table.stepwise <- as.data.frame(stepwise.all[, c(1, 5)])
table.stepwise[, 1] <- exp(table.stepwise[, 1])
colnames(table.stepwise) <- c("Rate ratio", "p.value")
rownames(table.stepwise) <- replace.names(rownames(table.stepwise))

table.stepwise$p.value <- pvalue.latex(table.stepwise$p.value)

pander(table.stepwise, table.style="multiline",
       # split.cells=c(5, 5, 5, 5, 5, 5, 5), 
	   digits=c(3, 1), 
	   split.table="Inf",
       caption="\\label{tab:stepwise}Stepwise regression: variables retained in model for severe disease")

@@

>>>>

---
title: 'Risk factors for severe COVID-19: a case-control study based on the Scottish population'
author: 
  - name: Paul M McKeigue
    email: paul.mckeigue@ed.ac.uk
    affiliation: Usher
  - name: Amanda Weir 
    affiliation: HPS
  - name: Jen Bishop
    affiliation: HPS
  - name: Stuart McGurnaghan
    affiliation: IGMM
  - name: Sharon Kennedy
    affiliation: HPS
  - name: Sharon Hutchinson 
    affiliation: GCU
  - name: David McAllister 
    affiliation: Glasgow
  - name: Chris Robertson 
    affiliation: Strathclyde
  - name: Rachael Wood
    affiliation: ISD
  - name: Nazir Lone
    affiliation: Usher
  - name: Tom Caparrotta 
    affiliation: IGMM
  - name: Helen M Colhoun
    affiliation: IGMM
address: 
   - code: Usher
     address: Usher Institute, College of Medicine and Veterinary Medicine, University of Edinburgh, Teviot Place, Edinburgh EH8 9AG, Scotland. PM - Professor of Genetic Epidemiology and Statistical Genetics. NL - Clinical Senior Lecturer in Critical Care
   - code: IGMM
     address: Institute of Genetics and Molecular Medicine, College of Medicine and Veterinary Medicine, University of Edinburgh, Western General Hospital Campus, Crewe Road, Edinburgh EH4 2XUC, Scotland. HC - Axa Chair in Medical Informatics and Epidemiology. TC - Sir George Alberti Doctoral Fellow in Pharmacoepidemiology. 
   - code: Glasgow
     address: Institute of Health and Wellbeing, University of Glasgow, 1 Lilybank Gardens, Glasgow G12 8RZ. DM - Senior Clinical Lecturer in Public Health 
   - code: HPS
     address: Health Protection Scotland (Public Health Scotland), Meridian Court, 5 Cadogan Street, Glasgow G2 6QE
   - code: Strathclyde
     address: Department of Mathematics and Statistics, University of Strathclyde, 16 Richmond Street, Glasgow G1 1XQ. CR - Professor of Public Health Epidemiology
   - code: GCU
     address: School of Health and Life Sciences, Glasgow Caledonian University. SH - Professor of Epidemiology and Population Health 
   - code: ISD
     address: NHS Information Services Division (Public Health Scotland), Gyle Square, 1 South Gyle Crescent, Edinburgh, EH12 9EB.  RW - Consultant in Maternal and Child Health.

@@

header-includes: |
  \let\origquote\quote
  \def\quote{\origquote\itshape}
  \usepackage{graphicx}
  \usepackage{longtable}
  \usepackage{booktabs}
  \usepackage{float}
  \usepackage{array}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{lscape}

output: 
#  pdf_document:
  rticles::plos_article:
    latex_engine: lualatex
    fig_caption: true
    keep_tex: true
#    toc: true
#    toc_depth: 2
csl: ../plos.csl
urlcolor: red

@@

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

library(knitr)
library(kableExtra)

@@

# Abstract

_Objectives_: to investigate risk factors for severe COVID-19 in the population.  Specifically, we wish to establish how far the association of severe disease with pre-existing morbidity is accounted for by a few circumscribed conditions that confer high vulnerability, rather than by associations with poor health that span multiple disease categories. Other objectives were to identify any drug exposures that are independently associated with high or low risk, and to assess the performance of a risk classifier constructed from medical records to discriminate between those at high and low risk for severe disease

_Methods_: age-sex-matched case-control study of severe disease, with each case matched to 10 controls registered with the same primary care practice.

_Results_:

* No new conditions associated with high risk independently of age and general health.

* Drug exposures unexpectedly associated with high risk: anticoagulants

* Performance of a risk classifier: at least 1.0 bits independently of age and sex

* A rule-based classifier based on ... can extract XX% of the information obtained from a model-based classifier.

_Conclusions_- These results show that risk stratification based on medical records can discriminate better than relying on age plus a list of conditions that confer highly vulnerable status.  They lay the basis for policies based on stratify and shield.

@@

te that at this point we are not including high risk of exposure as covariates ie HCW, residential care home, prisoner etc this will form part of future work.

@@

```{r agegr, echo=FALSE, warning=FALSE, message=FALSE}

rownames(table.agegr) <- replace.names(rownames(table.agegr))
knitr::kable(table.agegr,
             escape=TRUE, 
             booktabs=TRUE,
             label="agegr",
             align=rep("c", 8), 
             caption="Associations of severe disease with health status by age group") %>%
    column_spec(column=1, width="3.5cm") %>%
    group_rows("Hospital discharge diagnoses", 3, 6) %>%
    add_header_above(c(" "=1, "0-34 years"=2, "35-54 years"=2,
                       "55-74 years"=2, "75+ years"=2)) %>%
    landscape()

@@

```{r demog, echo=FALSE, warning=FALSE, message=FALSE}

table.demog.aug <- combine.tables3(table.demog, univariate.demog, multivariate.demog)
rownames(table.demog.aug) <- replace.names(rownames(table.demog.aug))
knitr::kable(table.demog.aug,
             escape=TRUE, 
             booktabs=TRUE,
             label="demog",
             digits=c(0, 0, 0, 20, 0, 100), 
             col.names=c(colnames(table.demog.aug)[1:2],
                         "Rate ratio (95% CI)", "p-value",
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with demographic factors") %>%
    column_spec(column=1, width="4cm") %>%
    group_rows("Ethnicity", 1, 2) %>%
    group_rows("SIMD quintile", 3, 6) %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

table.conditions.aug <- combine.tables3(table.conditions, univariate.conditions,
                                        multivariate.conditions)
rownames(table.conditions.aug) <- replace.names(rownames(table.conditions.aug))
knitr::kable(table.conditions.aug,
             escape=TRUE, 
             booktabs=TRUE,
             label="conditions",
             digits=c(0, 0, 0, 100, 0, 100), 
             col.names=c(colnames(table.conditions.aug)[1:2],
                         "Rate ratio (95% CI)", "p-value",
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with pre-existing conditions") %>%
    column_spec(column=1, width="4cm") %>%
    group_rows("Diabetes", 2, 4) %>%
    group_rows("ICD-10 chapter", 5, nrow(table.conditions.aug)) %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

table.drugs.aug <- combine.tables3(table.drugs, univariate.drugs, multivariate.drugs)
rownames(table.drugs.aug) <- replace.names(rownames(table.drugs.aug))
knitr::kable(table.drugs.aug,
             escape=TRUE, 
             booktabs=TRUE,
             label="drugs",
             digits=c(0, 0, 0, 100, 0, 100), 
             col.names=c(colnames(table.drugs.aug)[1:2],
                         "Rate ratio (95% CI)", "p-value",
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with prescribed drugs") %>%
    column_spec(column=1, width="4.5cm") %>%
    group_rows("BNF chapter", 2, nrow(table.drugs.aug)) %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

table.stepwise <- as.data.frame(stepwise.all[, c(1, 5)])
table.stepwise[, 1] <- exp(table.stepwise[, 1])
table.stepwise[, 1] <- round(table.stepwise[, 1], 2)
table.stepwise[, 2] <- signif(table.stepwise[, 2], 1)
rownames(table.stepwise) <- replace.names(rownames(table.stepwise))

# table.stepwise$p.value <- pvalue.latex(table.stepwise$p.value)

knitr::kable(table.stepwise,
             booktabs=TRUE,
             escape=TRUE,
             col.names=c("Rate ratio", "p-value"), 
             label="stepwise",
             align=rep("c", 2),
             caption="Stepwise regression: variables retained in model for severe disease") %>%
    group_rows("Diabetes", 3, 5)

@@

# Appendix

# Supplementary tables

```{r icdchapter1, echo=FALSE}
i <- 1
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r icdchapter2, echo=FALSE}
i <- 2
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r icdchapter3, echo=FALSE}
i <- 3
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r icdchapter4, echo=FALSE}
i <- 4
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter5, echo=FALSE}
i <- 5
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter6, echo=FALSE}
i <- 6
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter7, echo=FALSE}
i <- 7
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter8, echo=FALSE}
i <- 8
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter9, echo=FALSE}
i <- 9
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter10, echo=FALSE}
i <- 10
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter11, echo=FALSE}
i <- 11
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter12, echo=FALSE}
i <- 12
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter13, echo=FALSE}
i <- 13
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```{r icdchapter14, echo=FALSE}
i <- 14
knitr::kable(tables.icd.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("icdchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with conditions in ICD-10 chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()

#################### BNF chapters ############################

```{r bnfchapter1, echo=FALSE}
i <- 1
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter2, echo=FALSE}
i <- 2
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter3, echo=FALSE}
i <- 3
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter4, echo=FALSE}
i <- 4
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter5, echo=FALSE}
i <- 5
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter6, echo=FALSE}
i <- 6
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter7, echo=FALSE}
i <- 7
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter8, echo=FALSE}
i <- 8
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter9, echo=FALSE}
i <- 9
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter10, echo=FALSE}
i <- 10
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter11, echo=FALSE}
i <- 11
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter12, echo=FALSE}
i <- 12
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter13, echo=FALSE}
i <- 13
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

```{r bnfchapter14, echo=FALSE}
i <- 14
knitr::kable(tables.bnf.list[[i]],
             escape=TRUE, 
             booktabs=TRUE,
             label=paste0("bnfchapter", i),
             col.names=c(colnames(tables.icd.list[[i]])[1:2],
                         "Rate ratio (95% CI)", "p-value"),
             align=rep("c", 4), 
             caption=paste("Univariate associations with drug sections in BNF chapter", i)) %>%
    column_spec(column=1, width="8cm") %>%
    landscape()
```

## Comorbidities of initial interest

​
## Other recent health care exposure variables of interest are
